### 2023-06-25 Draft.tex
Added footnotes

\subsection{Typical applications of Non-Linear filters}
The subject of where one can apply Non-Linear filters has already been touched upon. Likely, the most prominent application area of non-linear filters in image processing is in noise filtering. Filtering away noise can be invaluable for increasing the clarity of a given image. A further application of non-linear filters is edge detection. Edge detection can be of vital importance (quite literally) in image processing, especially when applied in the context of computer vision, and for instance, autonomous cars. Non-Linear filters may also help in image enhancement and restoration, mostly through aforementioned applications such as noise-removal, pattern recognition (edge detection/segementation) and further techniques such as increasing contrast. Image restoration and enhancement can even be used to increase the resolution (upscaling) of images and videos, allowing old films to be re-released in higher resolutions. From the old graininess of VHS to HD and full HD all the way to UHD and 4k/8k resolutions. This process is of course not magic though, and it cannot create something that does not exist, hence it also cannot recover completely lost information\cite{sharmila}
\begin{figure}{H}
    \centering
    \includegraphics[width=1\linewidth]{upscaling.PNG}
    \caption{Non-Linear filtering can be a vital component in image enhancement and upscaling. In this photo the image has been upscaled from 64x64 to an impressive 1024x1024}
    \label{fig:enter-label}
\end{figure}

@@

Even with all the potential drawbacks that filtering can bring, the pros most likely heavily outweigh the cons. As technology advances, new techniques and new equipment will lead to even more advanced image processing. With the advent of AI, many of it's techniques may be appended to already existing techniques, or spawn new ones entirely. This will all surely lead to even more advanced filtering techniques, and with the blistering increase of data (big data) out there, there is no lack in training data for all AI/ML/Neural Network's needs. This will probably be the most major source of improvement for future filtering techniques. Another important area of improvement is efficiency. Increased hardware performance will lead to faster filtering algorithms working even more efficiently. Further research, and development of the algorithms will also lead to a better (lower) time-complexity, hence increasing the filtering algorithms efficiency further. This is of the utmost importance in, for instance, computer vision for autonomous cars. Faster processing and filtering of the image data a self-driving car collects can be the difference between life and death, and can drastically improve the safety of these self-driving cars.

>>>>

\subsection{Typical applications of Non-Linear filters}
The subject of where one can apply Non-Linear filters has already been touched upon. Likely, the most prominent application area of non-linear filters in image processing is in noise filtering. Filtering away noise can be invaluable for increasing the clarity of a given image. A further application of non-linear filters is edge detection. Edge detection can be of vital importance (quite literally) in image processing, especially when applied in the context of computer vision, and for instance, autonomous cars. Non-Linear filters may also help in image enhancement and restoration, mostly through aforementioned applications such as noise-removal, pattern recognition (edge detection/segementation) and further techniques such as increasing contrast. Image restoration and enhancement can even be used to increase the resolution (upscaling) of images and videos, allowing old films to be re-released in higher resolutions. From the old graininess of VHS to HD and full HD all the way to UHD and 4k/8k resolutions. This process is of course not magic though, and it cannot create something that does not exist, hence it also cannot recover completely lost information\cite{sharmila}\footnotemark\footnotetext{Entire Section of Non-linear Filters written by Alex}
\begin{figure}{H}
    \centering
    \includegraphics[width=1\linewidth]{upscaling.PNG}
    \caption{Non-Linear filtering can be a vital component in image enhancement and upscaling. In this photo the image has been upscaled from 64x64 to an impressive 1024x1024}
    \label{fig:enter-label}
\end{figure}

@@

Even with all the potential drawbacks that filtering can bring, the pros most likely heavily outweigh the cons. As technology advances, new techniques and new equipment will lead to even more advanced image processing. With the advent of AI, many of it's techniques may be appended to already existing techniques, or spawn new ones entirely. This will all surely lead to even more advanced filtering techniques, and with the blistering increase of data (big data) out there, there is no lack in training data for all AI/ML/Neural Network's needs. This will probably be the most major source of improvement for future filtering techniques. Another important area of improvement is efficiency. Increased hardware performance will lead to faster filtering algorithms working even more efficiently. Further research, and development of the algorithms will also lead to a better (lower) time-complexity, hence increasing the filtering algorithms efficiency further. This is of the utmost importance in, for instance, computer vision for autonomous cars. Faster processing and filtering of the image data a self-driving car collects can be the difference between life and death, and can drastically improve the safety of these self-driving cars.\footnotemark\footnotetext{Written by Alex}
